When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases

### 2018-02-12 paper/paper.tex
A bit less wordy about KatsarouNT17's heuristics

\citet{DBLP:conf/edbt/KatsarouNT17} look at ``straggler'' queries, which they define
to be the small subset of queries that they observe taking much longer than others to solve. The
authors present an approach to address this perceived problem that they describe as novel: ``instead
of trying to come up with new algorithms for sub-iso testing, we utilize isomorphic query rewritings
and existing alternative algorithms in parallel''. Their first claim is that permuting graphs before
running the subgraph isomorphism algorithm can lead to ``wildly different'' execution times. They
note that VF2 does not define ``a strict order in which the nodes of the query are matched'', and so
permuting the graphs (for example, by using degree or label frequency information) before search can
sometimes give orders of magnitude improvements. The connection to variable- and value-ordering
heuristics is not noted, and no consideration is given to dynamic ordering
heuristics like ``smallest domain first'' \citep{DBLP:journals/ai/HaralickE80}.
Of the orderings proposed, those involving placing rare labels first are effectively poor
approximations to a static ``smallest domain at top of search first'' ordering, whilst the remainder
use degree as we did earlier in this paper. However, \citeauthor{DBLP:conf/edbt/KatsarouNT17} do not
investigate any algorithm which employs domains, let alone strong variable- or value-ordering
heuristics or all-different propagation, and do not consider that their apparent successes could be
due to VF2's weaknesses rather than an inherent property of \NP-completeness.

>>>>

\citet{DBLP:conf/edbt/KatsarouNT17} present approaches to improve the run times for what they call
``straggler queries''---the small subset of queries that they observe taking much longer than others
to solve.  They observe that permuting graphs (for example, by using degree or label frequency
information) before running the subgraph isomorphism algorithm can improve run times by orders of
magnitude. However, the connection between this approach and variable- and value-ordering heuristics
is not noted, and no consideration is given to dynamic ordering heuristics such as ``smallest domain
first'' \citep{DBLP:journals/ai/HaralickE80}.  Of the orderings proposed, those involving placing
rare labels first are effectively approximations to a static ``smallest domain at top of search
first'' ordering, whilst the remainder use degree as we did earlier in this paper.
\citeauthor{DBLP:conf/edbt/KatsarouNT17} do not investigate any algorithm which employs strong
variable- or value-ordering heuristics, all-different propagation, or even domains, and do not
consider that the apparent successes of their approach could be due to VF2's weaknesses rather than
an inherent property of \NP-completeness.
